---
title: "Diamond Price Prediction"
author: "dhyanesh babu"
date: "April 16, 2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This presentation contains documentation for the Diamond price prediction application.It can be found in the link [**here**] (https://dhyaneshbabu.shinyapps.io/DiamondPrice/)

This application is building linear regression model using `diamonds` data set and is predicting the price of a diamond based on the selected diamond characteristics .The application allows the user to select:

- Carat
- Cut
- Color

It  plot a linear regression line and predictes price of the diamond.

## Application dataset

The data used for this application is `diamonds` data set(in `ggplot2` package).
```{r echo=FALSE}
library(ggplot2)
```

```{r echo=FALSE}
summary(diamonds)

```
## Files and Github Repo

This application is build using the shiny package.

There are two files used to create the app.

- Server.R
- ui.R

Files are available in the github repo
https://github.com/dhyaneshbabu/DiamondPricePrediction

Application is availble in the link
https://dhyaneshbabu.shinyapps.io/DiamondPrice/

## Functionality 

Application plots the scatter plot with carat in the x axis and price in the y axis.
Regression line is draw on above.

when we select the  features of the diamond (carat, cut, color) , the dataset is filtered, and linear regression is  recalculated. 

The predicted price of the diamond is displayed on the screen.
